### 2019-07-23 3_implementation.tex
Edit implementation section.

We have implemented Task Bench in the 15 parallel and distributed
programming systems listed in Table~\ref{tab:systems}. We describe the
systems, and any salient details of their Task Bench implementations,
below.

>>>>

We have implemented Task Bench in the 15 parallel and distributed
programming systems listed in Table~\ref{tab:systems}. These include
traditional HPC programming models: MPI~\cite{MPI} (with bulk
synchronous and point-to-point communication) and MPI+X (with OpenMP
and CUDA); PGAS and actor models: Chapel~\cite{Chapel15},
Charm++~\cite{Charmpp93}, X10~\cite{X1005}; and newer task-based
systems: OmpSs~\cite{OmpSs11}, OpenMP~\cite{OpenMPSpec40} (with task
dependencies), PaRSEC (with \emph{parameterized task graphs}
(PTG)~\cite{PARSEC13} and \emph{dynamic task discovery}
(DTD)~\cite{PARSEC_DTD}), Realm~\cite{Realm14},
Regent~\cite{Regent15}, and StarPU~\cite{StarPU11}. Also, we consider
several systems used in large scale data analytics and workflows:
Dask~\cite{Dask15}, Spark~\cite{Spark10}, Swift/T~\cite{Wozniak13},
and TensorFlow~\cite{TensorFlow15}. We describe the systems, and any
salient details of their Task Bench implementations, in our
supplemental material.
